Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex
Aggiunta immagine indicatori

To obtain indicators that in normal conditions can be treated as i.i.d. realizations of a random variable we, detrend~\cite{Gustafsson2000} the indicator sequence by a temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial g(t)$. Detrended indicators are more suitable to be monitored by a confidence interval since, as shown in Figure REFERENCE\_TODO.b). However, a tampering yielding permanent changes in the indicators, as those in Figure REFERENCE\_TODO.a results in a single outlier in the detrended indicator~\eqref{eq:detrending}.

>>>>

To obtain indicators that in normal conditions can be treated as i.i.d. realizations of a random variable we, detrend~\cite{Gustafsson2000} the indicator sequence by a temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial g(t)$. Detrended indicators are more suitable to be monitored by a confidence interval since, as shown in Figure \ref{fig:indicatori}(b). However, a tampering yielding permanent changes in the indicators, as those in Figure \ref{fig:indicatori}(a) results in a single outlier in the detrended indicator~\eqref{eq:detrending}.

\begin{figure}[tb]
\centering
\label{fig:indicatori} 
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Behavior of the average norm of the gradient \textbf{(a)} and its detrending \textbf{(b)} in a sequence with a defocus event.
The tampering event come at $t = 600$.
As illustrated in \textbf{(a)}, even in the case in which there aren't tampering events, there is nonstationarity.
Detrending is done in order to preserve stationarity in normal situations.
Considering the detrending \textbf{(b)} persistent changes become instantaneous:
in particular there is a peak in the instant in which tampering begins.}
\end{figure}
